---
title: "Problem Set 3"
author: "YOUR NAME"
date: "Enter the date"
output: pdf_document
---


# Installing the required packages

```{r include=FALSE}
##install.packages("ggplot2")
##install.packages("reader")
##install.packages("dplyr")
##install.packages("tidyverse")
##install.packages("stringr")
##install.packages("htmlwidgets")
##install.packages("jtools")
##install.packages("fastDummies")
##install.packages("corrplot")
##install.packages("ggcorrplot")

install.packages("Rmisc")
install.packages('pander')



```

# Loading the required packages
 You need to reload the installed packages every time you start a new session using the library function:

```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(reader)
library(stringr)
library(forcats)
library(modelr)
options(na.action = na.warn)
library(magrittr)
library(fastDummies)
library(corrplot)
library(ggcorrplot)
library(hexbin)
library(descr)
library(Rmisc)
library(pander)
```

# Upload your data file
First upload the csv file to the bottom right corner window. Then the following code will upload that data into R. 
# Make sure to use setwd() to set your directory (the directory in which you saved the PS_3.csv file in your computer) if you are using RStudio Desktop
```{r include=FALSE}


#data <- read_csv("PS_3.csv")


```
# Data_PS_3 –HR Records

## Variable Definitions & Codes:

Variable      |    Definitions & Codes
--------------|------------------------ 
ID:			      |    Employee identification number   
Age:			    |    Age in years (rounded)                                                                    
Jlevel:	    	|	   Job Level (4 levels of seniority, Scale 1 to 4, 1= low, 4= high
Tenure:	    	|    Years of service in the current organization (rounded)
Performance_pre:  |	 Performance before training. Scale 1 to 10; 1 = extremely poor, 10= extremely high
Gender:		    | Male, Female 
Race:		      |	White; Nonwhite
Married: 	    |	N = 0; Y = 1
Training:	    |	Participated in any training/development programs in the past 6 months.	Y, N
JobSat_Pre:		    |	Job Satisfaction before training. Scale of 1 to 5; 1 = Strongly Dissatisfied, 5 = Strongly Satisfied 
Salary: 	  	|	Annual Salary (dollars)
Division    	|	HR, Finance, Marketing, IT
Absent_Pre	      |	Number of days absent per year (before training)
Turnover      |	Turnover intention in the next 6 months, Scale of 1 to 5, 1 = No intention to quit, 5= determined to leave within 6 months |
JobSat_Post: |	Job Satisfaction after training. Scale of 1 to 5; 1 = Strongly Dissatisfied, 5 = Strongly Satisfied 
Absent_Post	      |	Number of days absent per year (after training)
Performance_Post: |	 Performance after training. Scale 1 to 10; 1 = extremely poor, 10= extremely high

> You have drawn this sample from the employees in your organization.

> ### **Important Note**: Do not put your text within the R code chunks. Only the R codes should be in the grey chunks. Your text should be outside of the grey chuncks. Look at R markdown cheatsheet for more information on how to organize your text in rmarkdown.

# **Questions**

# For each of the following statements answer these 5 questions:
a) Graphically evaluate the hypothesized relationship (use only one appropriate graph of your choice and do not use correlation table) (0.5 point)
b) What are the hypothesis statements? (0.5 point)
c) What is the p-value? (0.5 point)
d) What is your statistical conclusion using a significance level of 5 percent? (0.5 point)
e) What is the practical conclusion? (0.5 point)


#### Statement 1. (2.5 Points)	


In this organization men on average have more training opportunities than women
```{r}

```



#### Statement 2. (2.5 Points)	


In this organization white employees on average have more training opportunities than non-white employees
```{r}


```



#### Statement 3. (2.5 Points)	


In this organization training has imcreased performance for trained employees compared to untrained employees. 
```{r}

```



#### Statement 4. (2.5 Points)	


In this organization training has reduced absenteeism for trained employees compared to untrained employees. 
```{r}

```



#### Statement 5. (2.5 Points)	


In this organization training has increased job satisfaction for trained employees compared to untrained employees.  
```{r}

```



#### Statement 6. (2.5 Points)	


In this organization, among employees who had training, job satisfaction has improved more for non-whites than whites.
```{r}

```



#### Statement 7. (2.5 Points)	


In this organization, among employees who had training, absenteeism has decreased more for women more than for men.
```{r}

```





#### Statement 8. (2.5 Points)	


In this organization, among employees who had training, performance has increased more for men more than for women.
```{r}

```


